Imputation of incomplete multilevel data

### 2024-02-29 manuscript.qmd
add ToC

---
title: "Imputation of incomplete multilevel data"
author: "Hanne Oberman"
format: html
---

# Outline

- motivation and intended audience
- the mice framework/package
- background info on missingness mechanisms etc.
- case study

@@

::: {.callout-info}
# why not distinguish between missingness mechanisms
explanation needed
:::

>>>>

---
title: "Imputation of incomplete multilevel data"
author: "Hanne Oberman and Gerko Vink"
format:
  html:
    toc: true
---

@@

::: {.callout-note}
# why not distinguish between missingness mechanisms
explanation needed
:::
